A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-04-19 for_submission/rvaught_2018.tex
updated Martin_2013_galaxy_SB

\textbf{In addition to TKRS 4389, a second detection of extended \ion{Mg}{2} emission is reported in \cite{Martin2013}. In this study, the authors spatially resolve extended \ion{Mg}{2} emission in the galaxy, 32016857, at a redshift of $z=0.9392$ with SFR of $\sim 80\msunperyr$. Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc eastward away from the galaxy continuum. In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy. The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux. We convert the extended flux to SB using a 1 arcsec$^2$ aperture.
Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxies TKRS 4389 and 32016857 vs. SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel). These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.}

>>>>

\textbf{In addition to TKRS 4389, a second detection of extended \ion{Mg}{2} emission is reported in \cite{Martin2013}. In this study, the authors spatially resolve extended \ion{Mg}{2} emission in the galaxy, 32016857, at a redshift of $z=0.9392$ with SFR of $\sim 80\msunperyr$. Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc, or 1.4\arcsec\ at redshift $z\sim 0.94$, eastward away from the galaxy continuum. In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy. The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux. Likewise to TKRS 4389: We calculate a SB for the extended \ion{Mg}{2} emission, assuming that the total extended \ion{Mg}{2} emission is $0.46\times2.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ is collected in an aperture of 1.4\arcsec\ times the the 1.2\arcsec\ Keck/LRIS slit-width. Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxies TKRS 4389 and 32016857 vs. SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel). These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.}
